\documentclass[]{exam}
\usepackage[utf8]{inputenc}
\usepackage{amsmath,amssymb}
\usepackage{multicol}
\usepackage{soul}
\usepackage[a4paper,width=150mm,top=25mm,bottom=25mm]{geometry}
\usepackage{graphicx}
% \title{Innopolis University \\ Essentials of Analytical Geometry and Linear Algebra~I
% \\ Midterm.}
% \date{October 30, 2020.}
\newenvironment{amatrix}[1]{%
  \left(\begin{array}{@{}*{#1}{c}|c@{}}
}{%
  \end{array}\right)
}

\begin{document}

\centering 

AGLA 1. 2022. Retake of MIDTERM. 35 points, 120 minutes
\bigskip

% \begin{tabular}{cc}
  \begin{tabular}[b]{|p{11cm}|c|}
  \hline
  Full name: & Group: \\ \hline
   &  \\ 
   & \\
   \hline
  \end{tabular}
\bigskip

\begin{tabular}[b]{|c|c|c|c|c|c|c|c|}
    \hline
    Task: & 1 & 2 & 3 & 4 & 5 & Extra & Total \\ \hline
    Score: &  &  &  &  &  & & \_\_\_\_ of 30 pts. \_\_  extra \\ \hline
\end{tabular}

\begin{flushleft}
    % \textbf{\Large{Rules:}}
    % \begin{enumerate}
    \textbf{In each sheet}, you \textbf{should} write your last name, first name, variant number, and group number in the \textbf{upper right} corner. Unsigned sheets or sheets without the information above will NOT BE graded.
    % \end{enumerate}
% I agree with 
\end{flushleft}

\begin{enumerate}

\item (6 points) 
Find the equation of the straight line concurrent with the lines $2x + 3y = 3$ and $x + 2y = 2$ and also concurrent with the lines $3x - y = 1$ and $x + 5y = 11$.

\item (6 points)  
There are three points $A(2\textbf{i} + 4\textbf{j} + 2\textbf{k}), B(3\textbf{i}), C(-2\textbf{i} + 1\textbf{j} - 5\textbf{k}))$. Find the equation of the triangle's altitude passing through the point $B$.

\item (6 points) Solve the system 
\begin{enumerate}
    \item \textbf{Aw} = \textbf{b}, 
    
    where 
    $\textbf{w} =\begin{bmatrix}
    x \\ y \\ z
    \end{bmatrix}$
    $
\textbf{A}=\begin{bmatrix}
1 & -3 & 1 \\
1 & -1 & -1 \\
5 & -13 & 13
\end{bmatrix}$, 
$
\textbf{b}=
\begin{bmatrix}
4 \\
2 \\
8
\end{bmatrix}$
.

\item Find rank of the matrix $A$.
\item Explain relative positions of the planes that correspond to equations.
\end{enumerate} 


\item (6 points)   
Points $P$ and $Q$ belong to sides $AB$ and $AC$ of a triangle $ABC$ respectively, and $AP : PB = 2 : 3 $, $AQ : QC =1 : 2$.
\begin{enumerate}
  \item Find the transition matrix from basis $\overrightarrow{AC},\ \overrightarrow{BC}$ to basis $\overrightarrow{BQ},\ \overrightarrow{PC}$.
  \item Find coordinates $(x'; y')$ of point $M$ in coordinate system $\overrightarrow{BQ},\ \overrightarrow{PC}$ given its coordinates $(x; y)$ in CS $\overrightarrow{AC},\overrightarrow{BC}$.
\end{enumerate}


\item (6 points) Diagonals of a rhombus intersect at point $M(2; 1)$, the longest of them being
parallel to a horizontal axis. The side of the rhombus equals 2 and its obtuse angle is $120^\circ$. Compose the equations of the sides of this rhombus in general form.


% % Amer , maybe as Extra? 
\item (Extra, 5 points) Find the condition that one of the lines given by $ax^2 + 2hxy + by^2 = 0$ may be perpendicular to one of the lines given by $a_1x^2 + 2h_1xy + by^2 = 0$. And draw the picture.


\end{enumerate}

\end{document}