\documentclass[a4paper,10pt]{article}
%\documentclass[a4paper,10pt]{scrartcl}

\usepackage[utf8]{inputenc}
\usepackage[russian]{babel} % Cyrillics!
\usepackage{cmap} % Copypastable cyrillics!
\usepackage{amsmath} % Multiline equations
\usepackage{amssymb} % Cool symbols (like |R)
\usepackage{mathtools} % Disable numbering equations by default
\mathtoolsset{showonlyrefs}
\usepackage{indentfirst} % Indent first paragraph in chapter
\usepackage{multicol}


\makeatletter
\renewcommand*\env@matrix[1][*\c@MaxMatrixCols c]{%
  \hskip -\arraycolsep
  \let\@ifnextchar\new@ifnextchar
  \array{#1}}
\makeatother

\newcommand{\T}{\textrm{T}}
\newcommand{\I}{{-1}}

\title{Class \#6}
\author{Anastasiya Puzankova}
\date{}

\usepackage{color}
\newcommand{\adv}[0]{\textcolor{red}{*}}


\begin{document}
%\maketitle
\section*{Analytical Geometry and Linear Algebra~I, \\ Class \#6}
\noindent\textbf{Innopolis University, October 2021}
\\

\section{Lines in plane}

\begin{enumerate}

\item
Find the slope of the line joining the points $(2, 3)$ and $(4, -5)$.

\item
Find the slope of the line $2x - 3y + 7 = 0.$

\item
Find the equation of the straight line, the portion of which between the axes is bisected at the point $(2, -5)$.

\item
Find the equation of the straight line passing through the intersection of the lines $3x - y = 5$ and $2x + 3y = 7$ and making an angle of $45^{\circ}$ with the positive direction of x-axis.

\item
Find the equation of the straight line concurrent\footnote{Lines are said to be cuncurrent if they are intersect at a single point} with the lines $2x + 3y = 3$ and $x + 2y = 2$ and also concurrent with the lines $3x - y = 1$ and $x + 5y = 11$.

\item
$A(4, 1)$, $B(7, 4)$, and $C(5, -2)$ are the vertices of a triangle. Find the line equation which is goes from $A$ and perpendicular to $BC$.

\end{enumerate}

\newpage
\section*{Analytical Geometry and Linear Algebra~I, \\ HW \#6}
\noindent\textbf{Innopolis University, October 2021}
\\

\begin{enumerate}

\item
Find the equation of the straight line making an angle $135^{\circ}$ with the positive direction of x-axis and cutting of an intercept 5 on the y-axis.

\item
Find the equation of the straight line cutting off the intercepts 2 and −5 on the axes.

\item
Find the equation of the straight line passing through the points $(7, −3)$ and cutting off equal intercepts on the axes.

\item
Find the equation of the straight line of the portion of which between the axes is divided by the point $(4, 3)$ in the ratio 2:3.

\item
Find the equations to the straight lines each of which passes through the point $(3, 2)$ and intersect the $x$ and $y$ axes at $A$ and $B$ such that $OA - OB = 2$.

\item
Prove that the triangle whose vertices are $(−2, 5)$, $(3, −4)$, and $(7, 10)$ is a right angled isosceles triangle. Find the equation of the hypotenuse.

\item
Find the equation of the straight line passing through the intersection of the lines $7x + 3y = 7$ and $2x + y = 2$ and cutting off equal intercepts on the axes.

\item
Find the equation of the perpendicular bisector of the line joining the points $(−2, 6)$ and $(4, −6)$.

\item
Find the equation of the line through the intersection of $2x + y = 8$ and $3x + 7 = 2y$ and parallel to $4x + y = 11$.


\end{enumerate}

\end{document}
